test

### 2025-06-30 phasegenome_out/doc/paper/test.Rmd
Manuscript update

---
title: Resolving gut microbiome networks within Chiropterans
authors:
  - name: Timothy J. Rogers
    department: Department of Bioinformatics
    affiliation: University of North Carolina
    location: Charlotte, NC 28223
    email: troger50@charlotte.edu
  - name: Laurel R. Yohe
    department: Department of Bioinformatics and Genomics
    affiliation: North Carolina Research Center (NCRC)
    location:  Kannapolis, NC 28081
    email:  lyohe1@charlotte.edu
  - name: Richard A. White ${^\dagger}$
    department: Department of Bioinformatics
    affiliation: University of North Carolina
    location: Charlotte, NC 28223
    email: rwhit101@charlotte.edu
abstract: |
  Enter the text of your abstract here.
keywords:
  - Chiropterans
  - microbiome
  - virome
  - metagenomics
bibliography: "`r rbbt::bbt_write_bib('references.bib', overwrite = TRUE)`" 
#bibliography: references.bib
biblio-style: unsrt
output: rticles::arxiv_article
geometry: margin=1.0in
font-size: 11pt
header-include:
  -\usepapackage(helvet)
  -\renewcommand*\familydefault{\sfdefault}

---
${\dagger}$ To whom correspondence should be addressed

@@

### MAGs
```{r, echo=FLASE}
# Quality and length of rarefied MAGs
mag_stats<-fread("/projects/raw_lab/projects/Bats/bat_gut_micro/phasegenome_out/data/results/tables/mag_stats.csv")
# Abudance information:
mag_fam_rel_abun<-fread("/projects/raw_lab/projects/Bats/bat_gut_micro/phasegenome_out/data/results/tables/mag_fam_rel_abun.csv")
phylum_rel_abun<-mag_fam_rel_abun%>%select(-V1,-class:-family)%>%
  aggregate(.~phylum,sum)
colSums(phylum_rel_abun[,-1])
```
* (AND) We recovered `r mag_stats[domain=="Archaea",.N]` Archaeal and `r mag_stats[mag_stats$domain=="Bacteria",.N]` Bacterial medium to high quality MAGs with $\geq$ `r paste0(round(min(mag_stats$completeness)),"%")` and $\lt$ `r paste0(round(max(mag_stats$contamination)),"%")` redundancy.
* (AND) Of these `r nrow(mag_stats)` MAGs, `r length(mag_stats$genome[mag_stats$completeness>=90 & mag_stats$contamination<10,])` were $\geq$ 90% complete and $\lt$ 10% redundant, while YY are of high quality as determined by parameters layed out in XXX et al. (** TABLE **).
* (AND) Bacillota, Actinomycetota, and Pseudomonadata were the predominate phylum across the gut microbiome within all 3 of the bat species.
* (AND) No significant differnces were found in the richness (Choa1) or evenness (Pielou's Index) of prokaryotic MAGs across the 3 bat species.
* (AND) db-RDA analysis revealed no significant differnce in the $B$-diversity of the prokaryotic MAGs across the 3 bat species.
\includegraphics{../data/results/figures/FigX_top10_most_abun_viral_taxa.pdf}
### vOTUs
```{r,echo=FALSE}

>>>>

---
title: "test"
output: html_document
date: "2025-03-03"
---

${\dagger}$ To whom correspondence should be addressed

@@

### MAGs
```{r, echo=FALSE}
# Quality and length of rarefied MAGs
mag_stats<-fread("../../data/results/tables/mag_stats.csv")
# Abudance information:
mag_fam_rel_abun<-fread("../../data/results/tables/mag_fam_rel_abun.csv")
phylum_rel_abun<-mag_fam_rel_abun%>%select(-V1,-class:-family)%>%
  aggregate(.~phylum,sum)
#colSums(phylum_rel_abun[,-1])
```
* (AND) We recovered `r mag_stats[domain=="Archaea",.N]` Archaeal and `r mag_stats[mag_stats$domain=="Bacteria",.N]` Bacterial medium to high quality MAGs with $\geq$ `r paste0(round(min(mag_stats$completeness)),"%")` and $\lt$ `r paste0(round(max(mag_stats$contamination)),"%")` redundancy.
* (AND) Of these `r nrow(mag_stats)` MAGs, `r length(mag_stats$genome[mag_stats$completeness>=90 & mag_stats$contamination<10,])` were $\geq$ 90% complete and $\lt$ 10% redundant, while YY are of high quality as determined by parameters layed out in XXX et al. (** TABLE **).
* (AND) Bacillota, Actinomycetota, and Pseudomonadata were the predominate phylum across the gut microbiome within all 3 of the bat species.
* (AND) No significant differnces were found in the richness (Choa1) or evenness (Pielou's Index) of prokaryotic MAGs across the 3 bat species.
* (AND) db-RDA analysis revealed no significant differnce in the $B$-diversity of the prokaryotic MAGs across the 3 bat species.

### vOTUs
```{r,echo=FALSE}
